MSD panels 1, 2 and 3 HVE Supernatant

### 2016-09-22 MSD_panels_1_2_3_HVE_sup_analysis.Rmd
knit for github

ggplot(merge24And3, aes(x = Donor, y = Assay))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0)+
  facet_wrap(~Virus)+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
```

@@

test = matrix(rnorm(200), 20, 10)
test[1:10, seq(1, 10, 2)] = test[1:10, seq(1, 10, 2)] + 3
test[11:20, seq(2, 10, 2)] = test[11:20, seq(2, 10, 2)] + 2
test[15:20, seq(2, 10, 2)] = test[15:20, seq(2, 10, 2)] + 4
colnames(test) = paste("Test", 1:10, sep = "")
rownames(test) = paste("Gene", 1:20, sep = "")

pheatmap(test)

>>>>

ggplot(merge24And3, aes(x = Donor, y = Assay))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus)+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
```

@@
